% this file is called up by thesis.tex
% content in this file will be fed into the main document

\chapter*{List of Publications} % top level followed by section, subsection
\addcontentsline{toc}{chapter}{List of Publications}

% ----------------------- paths to graphics ------------------------

% change according to folder and file names
\ifpdf
    \graphicspath{{7/figures/PNG/}{7/figures/PDF/}{7/figures/}}
\else
    \graphicspath{{7/figures/EPS/}{7/figures/}}
\fi


% ----------------------- contents from here ------------------------
\section*{Journals}
\begin{enumerate}
    \item Yunus, Andi Prademon, Nobu C. Shirai, Kento Morita, and Tetsushi Wakabayashi. ``Comparison of RNN-LSTM and Kalman Filter Based Time Series Human Motion Prediction." In Journal of Physics: Conference Series, vol. 2319, no. 1, p. 012034. IOP Publishing, 2022.
    \item Yunus, Andi Prademon, Kento Morita, Nobu C. Shirai, and Tetsushi Wakabayashi. ``Time Series Self-Attention Approach for Human Motion Forecasting: A Baseline 2D Pose Forecasting." In Journal of Advanced Computational Intelligence and Intelligent Informatics (JACIII), Vol.27, No.3, 2023.
\end{enumerate}


\section*{International Conferences}
\begin{enumerate}
    \item Yunus, Andi Prademon, Nobu C. Shirai, Kento Morita, and Tetsushi Wakabayashi. ``Human Motion Prediction by 2D Human Pose Estimation using OpenPose." In The International Workshop on Frontiers of Computer Vision (IW-FCV) 2020, 2020. 
    \item Yunus, Andi Prademon, Nobu C. Shirai, Kento Morita, and Tetsushi Wakabayashi. ``Time series human motion prediction using RGB camera and OpenPose." In International Symposium on Affective Science and Engineering ISASE2020, pp. 1-4. Japan Society of Kansei Engineering, 2020.
    \item Yunus, Andi Prademon, Nobu C. Shirai, Kento Morita, and Tetsushi Wakabayashi. ``Comparison of RNN-LSTM and Kalman Filter Based Time Series Human Motion Prediction." In The 5th International Conference on Engineering Technology 2021 (ICET 2021).
    \item Yunus, Andi Prademon, Kento Morita, Nobu C. Shirai, and Tetsushi Wakabayashi. ``Temporal-Spatial Time Series Self-Attention 2D \& 3D Human Motion Forecasting" 2023 IEEE International Conference on Industry 4.0, Artificial Intelligence, and Communications Technology (IAICT).
    
\end{enumerate}

% ---------------------------------------------------------------------------
% ----------------------- end of thesis sub-document ------------------------
% ---------------------------------------------------------------------------