% Thesis Acknowledgements ------------------------------------------------


%\begin{acknowledgementslong} %uncommenting this line, gives a different acknowledgements heading
\begin{acknowledgements}      %this creates the heading for the acknowlegments

I would like to express my deepest gratitude and appreciation to all those who have contributed to my journey and supported me along the way.

First and foremost, I am incredibly grateful to my mother and father, my brother Andi Prawirawan,  my sisters Anna Syafarina and Adita Agreni Yunus, and my wife Nurul Huda, for their unwavering love, encouragement, and understanding. They have been my pillars of strength, offering guidance and support during both the challenging and joyous moments of my life.

I am sending my greatest acknowledgment to my supervisors, Prof. Naoki Isu, Prof. Tetsushi Wakabayashi,  Assistant Prof. Kento Morita, and my special collaborator Nobu C. Shirai. They have been enabling me to this extent, giving me the best advice and support not only as an advisor but also as a family, a friend, and a companion.

Furthermore, To the teacher in Engineering Faculty in general, and in Information Engineering Department especially. Along with the very helpful department, faculty, and international relation office staff that gives me silky smooth problem-solving during my study.

Lastly, I would like to express my appreciation to friends who are more like family in Japan and in Indonesia. As well as I want to acknowledge the supportive community of the Indonesia Student Association or Persatuan Pelajar Indonesia (PPI) in Mie and in Japan.

To everyone who has played a role, big or small, in shaping who I am today, I offer my heartfelt thanks. Your contributions have left an indelible mark on my journey, and I am grateful for the support, guidance, and inspiration you have provided.

\end{acknowledgements}
%\end{acknowledgmentslong}

% ------------------------------------------------------------------------


